\songtitle{Summer Nights}
\begin{verse*}
\textbf{M}: Summer lovin' had me a blast
\textbf{F}: Summer lovin' happened so fast
\textbf{M}: I met a girl crazy for me
\textbf{F}: Met a boy cute as can be
\textbf{M \& F}: Summer days driftin' away
To ah, oh, those summer nights
\end{verse*}

\begin{verse*}
Uh well-a well-a well-a huh!
\end{verse*}

\begin{verse*}
\textbf{M}: Tell me more, tell me more
\textbf{M}: Did you get very far? 
\textbf{F}: Tell me more, tell me more
\textbf{F}: Like does he have a car?
\textbf{F}: Uh-huh uh-huh uh-huh uh-huh
\end{verse*}

\begin{verse*}
\textbf{M}: She swam by me, she got a cramp
\textbf{F}: He ran by me, got my suit damp
\textbf{M}: I saved her life, she nearly drowned
\textbf{F}: He showed off, splashing around
\textbf{M \& F}: Summer sun, something's begun
But ah, oh, those summer nights
\end{verse*}

\begin{verse*}
Uh well-a well-a well-a huh!
\end{verse*}

\begin{verse*}
\textbf{F}: Tell me more, tell me more
\textbf{F}: Was it love at first sight?
\textbf{M}: Tell me more, tell me more
\textbf{M}: Did she put up a fight?
\end{verse*}

\begin{verse*}
Uh-huh uh-huh uh-huh uh-huh
\end{verse*}

\begin{verse*}
\textbf{M}: Took her bowling in the arcade
\textbf{F}: We went strolling, drank lemonade
\textbf{M}: We made out under the dock
\textbf{F}: We stayed out 'til ten o'clock
\textbf{M \& F}: Summer fling, don't mean a thing
But ah, oh, those summer nights
\end{verse*}

\begin{verse*}
Whoa, whoa, whoa!
\end{verse*}

\begin{verse*}
\textbf{M}: Tell me more, tell me more
\textbf{M}: But you don't gotta brag
\textbf{F}: Tell me more, tell me more
\textbf{F}: 'Cause he sounds like a drag
\end{verse*}

\begin{verse*}
Shoo-bop bop, shoo-bop bop, shoo-bop bop, shoo-bop bop
Shoo-bop bop, shoo-bop bop, shoo-bop bop, yeah!
\end{verse*}

\begin{verse*}
\textbf{F}: He got friendly, holding my hand
\textbf{M}: Well, she got friendly down in the sand
\textbf{F}: He was sweet, just turned eighteen
\textbf{M}: Well, she was good, you know what I mean
\textbf{M \& F}: Summer heat, boy and girl meet
But ah, oh, those summer nights
\end{verse*}

\begin{verse*}
Whoa, whoa, whoa!
\end{verse*}

\begin{verse*}
\textbf{F}: Tell me more, tell me more
\textbf{F}: How much dough did he spend?
\textbf{M}: Tell me more, tell me more
\textbf{M}: Could she get me a friend?
\end{verse*}

\begin{verse*}
\textbf{F}: It turned colder, that's where it ends
\textbf{M}: So I told her we'd still be friends
\textbf{F}: Then we made our true love vow
\textbf{M}: Wonder what she's doing now
\textbf{M \& F}: Summer dreams ripped at the seams
But oh, those summer nights...
\end{verse*}
